---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  fig.width=12, 
  fig.height=3
)
```

# allespaletti

<!-- badges: start -->
<!-- badges: end -->

`allespaletti` contains various color palettes I find useful, particularly for communication research. This includes palettes for:

- beautiful plots both color-blind- and printer-friendly
- political parties
- social networking sites 
- communication associations

```{r, echo=FALSE, message=FALSE, warning=FALSE}
devtools::load_all(".")
```

## Installation

Install from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("joon-e/allespaletti")
```
## Use

Load the package:

```{r eval=FALSE}
library(allespaletti)
```

Palettes can then be added to `ggplot2` objects using custom `scale_fill_xxx` / `scale_color_xxx` functions. See below for all available palettes:

```{r, fig.height=6}
library(ggplot2)
diamonds %>% 
  ggplot(aes(x = cut, fill = cut)) +
  geom_bar() + 
  scale_fill_tol("vibrant")
```

Use `reverse = TRUE` to plot colors in reverse order or pass a vector of color names (see below) to `select` to create a custom order (useful for palettes with _meaningful_ colors like political party or sns colors):

```{r, echo=FALSE}
sns <- c("Facebook", "YouTube", "WhatsApp", "Instagram")

sns_users_april_2020 <- data.frame(
  sns = factor(sns, sns, sns),
  users = c(2498, 2000, 2000, 1000)
)
```

```{r, fig.height=6}
ggplot(sns_users_april_2020, aes(x = sns, y = users, fill = sns)) +
  geom_col() +
  scale_fill_sns(select = c("facebook", "youtube", "whatsapp", "instagram")) +
  labs(x = NULL, y = "Users (in millions)") +
  theme(legend.position = "none")
```


## Palettes

Plot title shows the palette name that can be passed to the respective `scale_fill_` / `scale_color_` function; printed color names can be used for the `select` argument.

### Paul Tol's color schemes

[Paul Tol](https://personal.sron.nl/~pault/) developed various qualitative, sequential, and divergent color schemes that are both beautiful and distinct for most people (e.g., various forms of color-blindness) and situations (screen, print-out, black and white copy).

The following palettes are available for `scale_fill_tol()` / `scale_color_tol()`:

#### Qualitative palettes

```{r tolqual, echo = FALSE}
display_palette(tol_palettes, "bright")
display_palette(tol_palettes, "high_contrast")
display_palette(tol_palettes, "vibrant")
display_palette(tol_palettes, "muted")
display_palette(tol_palettes, "pale")
display_palette(tol_palettes, "dark")
display_palette(tol_palettes, "light")
```

#### Diverging palettes

Use `discrete = FALSE` in the call to `scale_fill_tol()` / `scale_color_tol()` to use these scales for continuous data.

```{r toldiv, echo = FALSE}
display_palette(tol_palettes, "sunset")
display_palette(tol_palettes, "BuRd")
display_palette(tol_palettes, "PRGn")
```

#### Sequential palettes

Use `discrete = FALSE` in the call to `scale_fill_tol()` / `scale_color_tol()` to use these scales for continuous data.

```{r tolseq, echo = FALSE}
display_palette(tol_palettes, "YlOrBr")
display_palette(tol_palettes, "iridescent")
display_palette(tol_palettes, "rainbow14")
display_palette(tol_palettes, "rainbow23")
display_palette(tol_palettes, "smooth_rainbow")
```

### Politics

Palettes containing colors of political parties. 

The following palettes are available for `scale_fill_politics()` / `scale_color_politics()`:

#### German parties

```{r polger, echo = FALSE}
display_palette(politics_palettes, "german")
display_palette(politics_palettes, "german2")
display_palette(politics_palettes, "fckafd")
```

#### US parties

```{r polus, echo = FALSE}
display_palette(politics_palettes, "us")
display_palette(politics_palettes, "us2")
```

### Social networking sites

Palettes containing colors of social networking sites. 

The following palettes are available for `scale_fill_sns()` / `scale_color_sns()`:

```{r sns, echo = FALSE}
display_palette(sns_palettes, "sns")
```

### Communication associations

Palettes containing colors of communication associations. 

The following palettes are available for `scale_fill_comm()` / `scale_color_comm()`:

```{r comm, echo = FALSE}
display_palette(comm_palettes, "ica")
display_palette(comm_palettes, "dgpuk")
```
